%\documentclass[12pt]{scrreprt}
\documentclass[12pt]{report} 

% language may be romanian or english (default is english)
% type may be bachelor or master (default is bachelor)
\usepackage[language=english, type=bachelor]{style}

%\geometry{a4paper,top=2.5cm,left=3cm,right=2.5cm,bottom=2.5cm}
%in style
%controlling the appearance of your headers and footers
\usepackage{fancyhdr}
\pagestyle{fancy}
\lhead{}
\chead{}
\renewcommand{\headrulewidth}{0.2pt}
\renewcommand{\footrulewidth}{0.2pt}

\begin{document}

\specialization{COMPUTER SCIENCE}	
\title{Providing real-time information on mobile devices, using Progressive Web Apps}
\author{Pricop Laurențiu}
\supervisor{Lect. Dr. Dana Lupșa}
				
\maketitle

\cleardoublepage
SHORT DESCRIPTION (for ELL laboratory only, will be removed)
\vspace{0.5cm}
\hrule
\vspace{0.5cm}

Historically, providing an interface for the user on a mobile phone has presented itself as a choice between two options: a web application, or a native mobile application. However, numerous frameworks have risen up that attempt to bridge the gap and provide the benefits of both worlds. A study by Biørn-Hansen et. al. [1] attempts to compare different technologies for creating cross-platform mobile applications and provides arguments for why Progressive Web Apps (PWAs) are a viable solution for such cross-platform development.

The Romanian national passenger railway operator, CFR Călători SA, provides two methods of viewing real-time information about trains: a website [2] and a mobile app [3], which sit at the opposite poles of the mobile application "spectrum". There is much to gain from combining these two applications into a singular PWA architecture.

In this thesis, in light of lacking literature on the topic of PWAs [4], I attempt to showcase a number of features that PWAs are capable of, that could not be possible in a single application based on either a website or a native mobile app. These features are presented in an application that provides real-time location information about where a passenger is, in relation to their train itinerary, and enables obtaining itinerary information from sources other than manual input, such as ticket QR codes or Optical Character Recognition.

[1]: Biørn-Hansen A., Majchrzak T. and Grønli T. (2017). Progressive Web Apps: The Possible Web-native Unifier for Mobile Development

[2]: \url{https://www.cfrcalatori.ro/cum-cumpar-online/#1517325197560-cf0f95de-6186}

[3]: \url{https://www.cfrcalatori.ro/comunicate/instaleaza-aplicatia-mobila-cfr-calatori-mersul-trenurilor-si-bilete-online-si-poti-cumpara-bilete-de-tren-direct-de-pe-telefon/}

[4]: Mole, Patrick V. (2020). Progressive Web Apps: A Novel Way for Cross-Platform Development

\newpage
\thispagestyle{empty}
\mbox{}
\newpage
\pagenumbering{roman} 

\cleardoublepage
ABSTRACT
\vspace{0.5cm}	
\hrule
\vspace{0.5cm}	
%\cleardoublepage

Abstract: un rezumat în limba engleză cu prezentarea, pe scurt, a conținutului pe capitole, punând accent pe contribuțiile proprii și originalitate



\tableofcontents


\newpage
\pagenumbering{arabic}

\input{chapters/chapter1_introduction}
%\addcontentsline{toc}{chapter}{Introducere}
% \addcontentsline{toc}{chapter}{Introduction}

\input{chapters/chapter2}
\input{chapters/chapter3}
\input{chapters/chapter4}

\input{chapters/chapter6_conclusions}
%\addcontentsline{toc}{chapter}{Concluzii}
%\addcontentsline{toc}{chapter}{Conclusions}

\bibliography{references}

\end{document}